Visual narratives of the Covid-19 pandemic

### 2022-01-17 JDSSV_manuscript_knitr.Rnw
color -> colour to standardize, also visualisation

my_theme <- theme_bw() + 
  theme(plot.background = element_rect(fill = "transparent", color = NA), 
        panel.background = element_rect(fill = "transparent", color = NA), 
        legend.background = element_rect(fill = "transparent", color = NA),
        axis.text.y = element_text(angle = 90, hjust = 0.5)) 
theme_set(my_theme)
@

<<colorpal, include = F>>=
# Including this for temporary compatibility - we may want to use *shudder* viridis?
main_colors <- c("#d00000", "#f5f1e7", "#c7c8ca")

# use as accents
secondary_colors <- c("#001226", "#249ab5")

# These are only to be used for infographics/charts
tertiary_colors <- c("#bccb2a", "#f58a1f", "#005d84", "#ffd74f", "#a5228d")

color_palette <- c("#d00000", "#249ab5",  "#1B8500", "#f58a1f", "#a5228d", "#001226", "#B1EB66", "#005d84", "#c25700")

heat_color_palette <- c("#ffd74f", "#f58a1f", "#c25700", "#d00000", "#9D0000", "#6A0000")

@@

p1 <-  tmp %>%
  ggplot(aes(x = date, y = daily_avg_cases, group = state)) +
  geom_textline(aes(color = state, label = state, vjust = -0.1, hjust =.93) , text_smoothing = 50) + 
  ylab("Daily average cases (7 day average)") + 
  xlab("Date") + 
  guides(color = "none") + 
  scale_y_log10() + 
  facet_grid(~"Log") + 
  theme_bw()

p2 <-  tmp %>%
  ggplot(aes(x = date, y = daily_avg_cases, group = state)) +
  geom_textline(aes(color = state, label = state, vjust = -0.25, hjust = .85) , text_smoothing = 60) + 
  ylab("Daily average cases (7 day average)") + 
  xlab("Date") + 
  guides(color = "none") + 
  facet_grid(~"Linear") + 
  theme_bw() +
  theme(axis.title.y = element_blank())

@@

tmp %>%
ggplot(aes(x = x, y = value, color = name, size = name)) + 
  geom_line(alpha = .9) +
  facet_grid_sc(rows = vars(scale), cols = vars(Baseline), 
                scales = list(x = "fixed", y = scales_y)) +
  scale_size_manual(values = c(1.75, 1, 1)) +
  scale_color_manual(values = c("#249ab5", "#d00000", "#001226")) +
  scale_fill_discrete(name = "") + 
  theme_bw() + 
  theme(legend.position = "bottom", axis.title = element_blank(),
        legend.title = element_blank())
@

% Focus primarily on time-series graphs (as opposed to log scales in color)

@@

If necessary or useful, information about certain computational details
such as version numbers, operating systems, or compilers could be included
in an unnumbered section. Also, auxiliary packages (say, for visualizations,
maps, tables, \dots) that are not cited in the main text can be credited here.

>>>>

my_theme <- theme_bw() + 
  theme(plot.background = element_rect(fill = "transparent", colour = NA), 
        panel.background = element_rect(fill = "transparent", colour = NA), 
        legend.background = element_rect(fill = "transparent", colour = NA),
        axis.text.y = element_text(angle = 90, hjust = 0.5)) 
theme_set(my_theme)
@

<<colourpal, include = F>>=
# Including this for temporary compatibility - we may want to use *shudder* viridis?
main_colours <- c("#d00000", "#f5f1e7", "#c7c8ca")

# use as accents
secondary_colours <- c("#001226", "#249ab5")

# These are only to be used for infographics/charts
tertiary_colours <- c("#bccb2a", "#f58a1f", "#005d84", "#ffd74f", "#a5228d")

colour_palette <- c("#d00000", "#249ab5",  "#1B8500", "#f58a1f", "#a5228d", "#001226", "#B1EB66", "#005d84", "#c25700")

heat_colour_palette <- c("#ffd74f", "#f58a1f", "#c25700", "#d00000", "#9D0000", "#6A0000")

@@

p1 <-  tmp %>%
  ggplot(aes(x = date, y = daily_avg_cases, group = state)) +
  geom_textline(aes(colour = state, label = state, vjust = -0.1, hjust =.93) , text_smoothing = 50) + 
  ylab("Daily average cases (7 day average)") + 
  xlab("Date") + 
  guides(colour = "none") + 
  scale_y_log10() + 
  facet_grid(~"Log") + 
  theme_bw()

p2 <-  tmp %>%
  ggplot(aes(x = date, y = daily_avg_cases, group = state)) +
  geom_textline(aes(colour = state, label = state, vjust = -0.25, hjust = .85) , text_smoothing = 60) + 
  ylab("Daily average cases (7 day average)") + 
  xlab("Date") + 
  guides(colour = "none") + 
  facet_grid(~"Linear") + 
  theme_bw() +
  theme(axis.title.y = element_blank())

@@

tmp %>%
ggplot(aes(x = x, y = value, colour = name, size = name)) + 
  geom_line(alpha = .9) +
  facet_grid_sc(rows = vars(scale), cols = vars(Baseline), 
                scales = list(x = "fixed", y = scales_y)) +
  scale_size_manual(values = c(1.75, 1, 1)) +
  scale_colour_manual(values = c("#249ab5", "#d00000", "#001226")) +
  scale_fill_discrete(name = "") + 
  theme_bw() + 
  theme(legend.position = "bottom", axis.title = element_blank(),
        legend.title = element_blank())
@

% Focus primarily on time-series graphs (as opposed to log scales in colour)

\begin{figure}
\centering
\includegraphics[width=.8\linewidth]{ft-reference-lines}
\caption{An annotated time series from the Financial Times which appeared on Twitter on November 12, 2020. This chart has annotations which show the decreasing $R_{eff}$ in successive peaks of the pandemic, with periods of $R_{eff}<1$ between surges in cases. These annotations assist the reader with drawing complex conclusions from the chart, but are difficult to automate and thus tend to be manually curated. Source: Mark Gubrud (@mgubrud), \url{https://twitter.com/mgubrud/status/1326784082399944704}.}
\label{fig:log-scale-ref-multiple}
\end{figure}

@@

If necessary or useful, information about certain computational details
such as version numbers, operating systems, or compilers could be included
in an unnumbered section. Also, auxiliary packages (say, for visualisations,
maps, tables, \dots) that are not cited in the main text can be credited here.
